Endogenous model shifts in algorithmic recourse

### 2022-02-10 students/project_counterfactual_generators.qmd
updated the student project proposal

Individually, each of the students will then choose one of the recourse generators already implemented in [CARLA](https://github.com/carla-recourse/CARLA) and run a simple experiment (details below) to generate endogenous shifts and quantify their magnitude.

Collectively, the students will finally tackle the following questions:

- Does the magnitude of induced model shifts vary by recourse generator? 
- If so, what factors might be playing a role here?
- Based on your findings, what appear to be good ways to deal mitigate endogenous shifts?

@@

1. [Wachter](https://arxiv.org/ftp/arxiv/papers/1711/1711.00399.pdf)
2. [REVISE](https://arxiv.org/pdf/1907.09615.pdf)
3. [CEM](https://arxiv.org/pdf/1802.07623.pdf)
4. [CEM-VAE](https://arxiv.org/pdf/1802.07623.pdf)
5. [AR-LIME](https://arxiv.org/pdf/1809.06514.pdf)

@@

1. Train an algorithm $\mathcal{M}$ for a binary classification task. 
2. Determine a target class. Generate recourse for a share $\mu$ of randomly selected individuals in the other class to revise their label (i.e. move to the target class). Store some of the conventional benchmark measures readily implemented in CARLA (cost, success rate, ...)
3. Implement recourse for those indviduals and quantify the domain shift.
4. Retrain $\mathcal{M}$ and quantify the model shift.
5. Repeat steps 1-4 for $K$ rounds.

>>>>

Individually, each of the students will then choose one of the recourse generators already implemented in [CARLA](https://github.com/carla-recourse/CARLA) and run a simple experiment (details below) to generate endogenous shifts and quantify their magnitude.
You will also each produce results for the baseline generator ([Wachter](https://arxiv.org/ftp/arxiv/papers/1711/1711.00399.pdf)) and benchmark the results from both generators.

Use the results to answer the following questions with respect to your chosen generator:

- Does the magnitude of induced model shifts differ compared to the baseline generator? 
- If so, what factors might be playing a role here?
- Based on your findings, what appear to be good ways to mitigate endogenous shifts?

@@

1. [FACE](https://arxiv.org/pdf/1909.09369.pdf)
2. [REVISE](https://arxiv.org/pdf/1907.09615.pdf)
3. [CEM](https://arxiv.org/pdf/1802.07623.pdf)
4. [CEM-VAE](https://arxiv.org/pdf/1802.07623.pdf)
5. [AR-LIME](https://arxiv.org/pdf/1809.06514.pdf)

@@

1. Train an algorithm $\mathcal{M}$ for a binary classification task. 
2. Determine a target class. Using your chosen generator and the baseline generator ([Wachter](https://arxiv.org/ftp/arxiv/papers/1711/1711.00399.pdf)) generate recourse for a share $\mu$ of randomly selected individuals in the other class to revise their label (i.e. move to the target class). Store some of the conventional benchmark measures readily implemented in CARLA (cost, success rate, ...)
3. Implement recourse for those indviduals and quantify the domain shift.
4. Retrain $\mathcal{M}$ and quantify the model shift.
5. Repeat steps 1-4 for $K$ rounds.
